\documentclass[11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[margin=0.8in]{geometry}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage{xcolor}
\usepackage{titlesec}
\usepackage{longtable}

% Custom Colors
\definecolor{primary}{RGB}{37, 99, 235}
\definecolor{secondary}{RGB}{107, 114, 128}
\definecolor{success}{RGB}{22, 163, 74}
\definecolor{warning}{RGB}{217, 119, 6}
\definecolor{danger}{RGB}{220, 38, 38}

% Styling
\titleformat{\section}{\large\bfseries\color{primary}}{}{0em}{}[\titlerule]
\titleformat{\subsection}{\normalsize\bfseries\color{primary}}{}{0em}{}
\setlist[itemize]{noitemsep, topsep=2pt}
\setlist[enumerate]{noitemsep, topsep=2pt}

\title{\textbf{GoAccel Chatbot Platform \\ \large Comprehensive Project Documentation \& Implementation Status}}
\author{Tayyab Riaz \& Development Team}
\date{January 8, 2026}

\begin{document}

\maketitle

\section{Project Overview}
The \textbf{GoAccel Chatbot Platform} (formerly WarmProspect) enables businesses to create customized AI assistants. The system leverages Google Gemini AI for advanced natural language processing, supporting both multi-tenant text chat and real-time voice interactions, integrated with CRM capabilities.

\section{Core Architecture}
\subsection{Technology Stack}
\begin{itemize}
    \item \textbf{Backend Framework:} FastAPI (Python)
    \item \textbf{AI/ML Engine:} Google Gemini API (\texttt{gemini-2.5-flash} for chat, \texttt{gemini-2.0-flash-exp} for voice)
    \item \textbf{Database:} PostgreSQL (with JSON file fallback for portability)
    \item \textbf{Session Storage:} Redis (with In-memory fallback for local development)
    \item \textbf{Voice Services:} Twilio (Phone calls) \& Edge TTS (Text-to-Speech)
    \item \textbf{RAG Engine:} FAISS vector search with Google \texttt{text-embedding-004}
    \item \textbf{Deployment:} Docker, Render/VPS
\end{itemize}

\section{Implementation Status}

\subsection{\textcolor{success}{Completed Features (Production Ready)}}
\begin{itemize}
    \item \textbf{Multi-Tenant Business Management:} Full CRUD operations via Admin API/Panel.
    \item \textbf{Dynamic Branding:} Automatic UI skinning (GA Logo, Colors, Greetings) via \texttt{business\_id}.
    \item \textbf{AI Chat Engine:} Gemini Chat integration with automatic history management and strict formatting rules.
    \item \textbf{Session Management:} Isolated Redis-based storage using \texttt{business\_id:session\_id} keys.
    \item \textbf{RAG Integration:} Independent FAISS vector indexes per business with citation support.
    \item \textbf{CRM Framework:} Function-calling structure for contact and deal management.
    \item \textbf{Hard Guards:} Intro token detection and appointment-booking protection.
    \item \textbf{Stability Fixes:} Increased rate limits (20/min), cache-busting, and fetch error handling.
\end{itemize}

\subsection{\textcolor{warning}{Tasks In Progress (Current Focus)}}
\begin{itemize}
    \item \textbf{Twilio Voice Agent:} Framework is integrated with WebSocket streaming, currently undergoing latency optimization and live environment validation.
    \item \textbf{Multi-level CTA System:} Implementing hierarchical, context-aware CTA selection (Primary $\rightarrow$ Secondary $\rightarrow$ Tertiary).
    \item \textbf{Production Hardening:} Transitioning to structured logging (\texttt{structlog}) and enforcing strict Redis usage for deployment.
\end{itemize}

\subsection{\textcolor{danger}{Future Roadmap (Pending)}}
\begin{itemize}
    \item \textbf{Real CRM Integration:} Replacing placeholder tools with live Salesforce/HubSpot API connectors.
    \item \textbf{RAG Enhancements:} Real-time knowledge base updates and multi-modal support (PDFs/Images).
    \item \textbf{Advanced AI:} Intent classification, sentiment analysis, and multi-turn conversation planning.
    \item \textbf{Testing:} Comprehensive Unit, Integration, and End-to-End (E2E) testing suites.
\end{itemize}

\section{Data Flow}
\subsection{Chat Request Flow}
\texttt{User Message $\rightarrow$ FastAPI /chat $\rightarrow$ Load Config (PostgreSQL) $\rightarrow$ Build Instructions $\rightarrow$ Get Chat Session (Gemini SDK) $\rightarrow$ RAG Retrieval $\rightarrow$ Send to Gemini $\rightarrow$ Handle Function Calls $\rightarrow$ Return Response}

\subsection{Voice Request Flow (Twilio)}
\texttt{Incoming Call $\rightarrow$ Twilio Webhook $\rightarrow$ FastAPI /voice/incoming $\rightarrow$ TwiML Response $\rightarrow$ WebSocket /media-stream $\rightarrow$ Gemini Live API $\rightarrow$ Audio Response $\rightarrow$ Twilio WebSocket $\rightarrow$ Phone Call}

\section{API Endpoints}
\begin{itemize}
    \item \textbf{Public:} \texttt{POST /chat}, \texttt{GET /api/business/\{id\}/config}, \texttt{GET /health}
    \item \textbf{Admin (Protected):} \texttt{POST /admin/business}, \texttt{GET /admin/business}, \texttt{DELETE /admin/business/\{id\}}
    \item \textbf{Voice:} \texttt{POST /voice/incoming}, \texttt{WebSocket /media-stream}
\end{itemize}

\section{Feedback Response}
The feedback from the Team Lead has been thoroughly reviewed. The transition to the \textbf{GoAccel} branding is complete. The immediate priority is the stabilization of the \textbf{Twilio Voice Agent} and the implementation of \textbf{Dynamic CTA Logic} to move the platform from static configurations to a truly adaptive AI experience.

\end{document}
